### 2015-01-19 src/methodology.Rnw
add varreduction

\subsubsection{Constrained Mutation}
\noindent\textbf{Wong et al. ~\cite{wong1995reducing}.} They selected ROR
and ABS from Mothra for mutation analysis. The ABS operator was chosen with
the reasoning that it forces users to consider all parts of the input domain,
and ROR was chosen because it forces users to consider values of predicates.
ROR mutates relational operators, while ABS replaces variables and expressions
by their positive or negative absolute value or zero. \Pitcb and \Pitnc from
PIT are a good map for ROR. However, we could not map ABS to PIT operators.

@@

\subsubsection{E-Selective}
\noindent\textbf{Offut et al. \cite{offutt1996anexperimental}.} They selected
ABS, UOI, LCR, AOR, ROR from Mothra operators.  We have used  \Pitin, \Pitm,
\Pitcb, and \Pitnc. PIT does not have any operator comparable to LCR.

@@

\subsubsection{Variable Reduction}
\noindent\textbf{Namin et al.~\cite{siami2008sufficient}.}
They have tried to reduce the mutation operators of Proteum analysis
tool which is for C programs. They suggest 28 operators which many of them
are not applicable in Java, and some not in PIT.
We  used by  \Pitin, \Pitm, \Piti, and \Pitnc.

@@

\subsubsection{Statement deletion emulation} \label{subsec:stmtdel}
The original statement deletion was proposed by Acree~\cite{acree1980onmutation}.

The statement deletion based operator selection was based on the work by
Deng et al.~\cite{deng2013empirical}. The operations on single
statements were modeled using \Pitvmc, \Pitnvmc, \Pitcc, \Pitemv, and
\Pitri~for simple statements, and using \Pitrc for control structures. \Pitrc
replaces boolean conditions with \textit{false}, resulting in removal of the
conditional block. The operator for return values was modeled using
\Pitrv, which is similar.  The operators for \textit{while},
\textit{for}, and \textit{if} statements were modeled using \Pitdc,
which replaced the boolean condition with \textit{true}, which removed the
effect of conditional. The \textit{switch} statement deletion was
modeled using \Pitrs which replaced the first 100 labels with a
\textit{default} label, resulting in the switch element being
deleted. Due to the constraints of the architecture of PIT only the
first 100 labels were replaced. Deleting \textit{try/catch} was not
necessary at bytecode level.

>>>>

\subsubsection{Constrained Mutation}
\noindent\textbf{Wong et al. ~\cite{wong1995reducing}.} They selected ROR
and ABS from Mothra for mutation analysis. The ABS operator was chosen with
the reasoning that it forces users to consider all parts of the input domain,
and ROR was chosen because it forces users to consider values of predicates.
ROR mutates relational operators, while ABS replaces variables and expressions
by their positive or negative absolute value or zero. \Pitcb and \Pitnc from
PIT are a good map for ROR. Similarly, \Pitin is able to partially provide ABS
functionality.

@@

\subsubsection{E-Selective}
\noindent\textbf{Offut et al. \cite{offutt1996anexperimental}.} Mothra supports
three main classes of operators; operand mutators, operator (expression)
mutators and statement mutators. The E-Selective strategy chooses only those
mutators that modify operators. These for Mothra were ABS, UOI, LCR, AOR, and
ROR. UOI operates by incrementing or decrementing arithmetic expressions by 1,
LCR changes the relational operators, and AOR mutates arithmetic operators.

% UOI : Unary insertion : toggle +1, -1
% LCR : Logical connectives : a && b -> a || b, a, b, T, F
% AOR : Arithmetic a + b ->  a - b, *,%,a,b

For mapping to PIT, we have tried to follow the spirit of choosing only
operator mutators form the mutators available in PIT. The operators we have
used are \Pitin, \Pitm, \Pitcb, \Pitnc, \Pitrc, and \Pitnc.

@@

\subsubsection{Variable Reduction}
\noindent\textbf{Namin et al.~\cite{siami2008sufficient}.}
For variable reduction, Namin framed the question of finding the best set of
mutation operators as a statistical problem of finding the set of operators
such that we can best predict the final mutation score. That is, given that
$M$ is the final mutation score, and $m_1,m_2..m_n$ are mutation scores given
by $n$ mutation operators, Namin wanted to find the smallest set of mutations
such that we can predict $M$ from the set of $m_{1..n}$. This boils down to
finding the linear model

\[M = \alpha m_1 + \beta m_2 ... \omega m_n\]

where $\alpha,\beta .. \omega$ are constants. However we take advantage of the
limited set of operators to run a complete subset model comparison to obtain
the best model given by
\[\mu{M_s} = 0+.55 nmc + .2 rc + .1 dc + .2 rv + .1 cc + .7emv + .02 m + .02 ri \]

with $R^2 = 0.96$. This suggests that the variables we should be interested
in are \Pitnvmc, \Pitrc, \Pitdc, \Pitrv, \Pitcc, \Pitemv, \Pitm, \Pitri

\begin{comment}
Call:
lm(formula = x ~ xnmc + xrc + xdc + xrv + xcc + xemv + xm + xri)

Residuals:
     Min       1Q   Median       3Q      Max 
-0.12643 -0.01446 -0.00313  0.00768  0.52589

Coefficients:
             Estimate Std. Error t value Pr(>|t|)    
(Intercept)  0.003130   0.004537   0.690  0.49083    
xnmc         0.549245   0.031977  17.176  < 2e-16 ***
xrc          0.197321   0.037466   5.267 2.64e-07 ***
xdc          0.067979   0.027314   2.489  0.01336 *  
xrv          0.205544   0.028226   7.282 2.87e-12 ***
xcc         -0.074420   0.023555  -3.159  0.00174 ** 
xemv         0.071699   0.020909   3.429  0.00069 ***
xm           0.022937   0.015159   1.513  0.13131    
xri         -0.026070   0.016472  -1.583  0.11453    
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

Residual standard error: 0.05318 on 302 degrees of freedom
Multiple R-squared:  0.9669,  Adjusted R-squared:  0.9661 
F-statistic:  1104 on 8 and 302 DF,  p-value: < 2.2e-16

\end{comment}

%The variable reduction procedure given by Namin results in 28 operators of
%Proteum analysis tool. Unfortunately for us, unlike the previous selection
%techniques

%They have tried to reduce the mutation operators of Proteum analysis
%tool which is for C programs. They suggest 28 operators which many of them
%are not applicable in Java, and some not in PIT.
%We used \Pitin, \Pitm, \Piti, and \Pitnc.

@@

\subsubsection{Statement deletion emulation} \label{subsec:stmtdel}
The statement deletion based operator selection was based on the work by
Deng et al.~\cite{deng2013empirical}. The operations on single
statements were modeled using \Pitvmc, \Pitnvmc, \Pitcc, \Pitemv, and
\Pitri~for simple statements, and using \Pitrc for control structures. \Pitrc
replaces boolean conditions with \textit{false}, resulting in removal of the
conditional block. The operator for return values was modeled using
\Pitrv, which is similar.  The operators for \textit{while},
\textit{for}, and \textit{if} statements were modeled using \Pitdc,
which replaced the boolean condition with \textit{true}, which removed the
effect of conditional. The \textit{switch} statement deletion was
modeled using \Pitrs which replaced the first 100 labels with a
\textit{default} label, resulting in the switch element being
deleted. Due to the constraints of the architecture of PIT only the
first 100 labels were replaced. Deleting \textit{try/catch} was not
necessary at bytecode level.
